---
title: "What this package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What this package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753F25johnson)
```

# Introduction

This package was made for the course MATH 4753 at the University of Oklahoma. Its contents include various functions, apps and data sets that have been created and used throughout the course. Below, you will find several functions that can be used with this package.

# Functions

## myfirstfunction()

This is the first function that has been added to the package. Its use case is simple. All it does is take a list of x values and output the square of each, plotting them also.

```{r}
myfirstfunction(1:10)
```

## mysum()

This function doesn't do anything but output what the function `summary()` outputs. This function was made strictly to get a feel for how functions are made and added to a package.

```{r}
mysum(1:10)
```

## scatterhist()

This function creates a scatter plot with marginal histograms for each parameter. 

```{r}
scatterhist(ddt$LENGTH, ddt$WEIGHT)
```

## mysample()

This function creates `iter` samples of size `n`, randomly selecting from values 1 through 10 of equal probability. The function outputs a bar chart showing the distribution.

```{r}
mysample(10000)
```

## myncurve()

This function takes a normal distribution and a given lower tail. It returns a plot of the distribution and lower tail with its probability, and also returns the input values.

```{r}
myncurve(0,1,1)
```

## ntickets()

This function comes from the overbooking problem. This function serves as a solution to the problem for most given values.
**NOTE**: This function has been tested for most extreme input values *except* for gamma. When I created this function, I forgot to account for changes in gamma; however, this function should work well for non-extreme values of gamma.

```{r, fig.height=8,fig.width=8}
ntickets(200, 0.02, 0.95)
```

## mycltu()

This function is used to show the central limit theorem by taking `iter` samples of size `n`. The output gives a plot that shows the expected density function and the actual density curve, as well as a histogram of the density. There is also a black line to indicate the uniform density plot.

```{r}
mycltu(20,10000)
```

## myboot2()

This function is for bootstrapping a random sample to make many more random samples. It outputs the confidence interval, the x statistic, and some input values. It also plots the data.

```{r}
myboot2(x = rnorm(30,8,10))
```

## shinymle()

This is the last function presented in this package. This function was created by ChatGPT. It uses a shiny app for the Maximum Likelihood Estimate (MLE). An example is not displayed as the app cannot be opened, but you can run the function yourself to see what it does.

```{r,eval=FALSE}
shinymle()
```

